Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)

### 2023-11-07 manuscript_BiSC.tex

In this study, within the framework of the Barcelona Life Study Cohort (BiSC), we developed and compared LUR, DM, and HM models to estimate outdoor air pollution exposure at residential addresses. LUR and DM, were constructed using conventional state-of the art techniques, HM was innovetely designed by harnessing RF algorithm, integrating outputs from DM with explanatory variables from the LUR model. The overall aim is to obtain accurate NO\textsubscript{2}, PM\textsubscript{2.5}, PM\textsubscript{2.5} constituents (Fe, Zn, Cu, Sb), and BC estimates, intended to use in the prenatal exposure assessment within the BiSC cohort. Additionally, we aim to evaluate the impact of the COVID-19 pandemic on these outdoor air pollution exposure assessments.

>>>>

In this study, within the framework of the Barcelona Life Study Cohort (BiSC), we developed and compared LUR, DM, and HM models to estimate outdoor air pollution exposure at residential addresses. LUR and DM, were constructed using conventional state-of the art techniques, while HM was innovetely designed by harnessing RF algorithm, integrating outputs from DM with explanatory variables from the LUR model. The overall aim is to obtain accurate NO\textsubscript{2}, PM\textsubscript{2.5}, PM\textsubscript{2.5} constituents (Fe, Zn, Cu, Sb), and BC estimates, intended to use in the prenatal exposure assessment within the BiSC cohort.
